Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-15 tensor/draft/draft-tensor-op.tex
[draft] revise conclusions and acknowledgements

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
\caption{ The sensitivity to the tensor coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available.
      }
  \label{fig:FHvsCT}
\end{figure*}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Fits and constraints
  \label{sec:results}
}

@@

A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in cartesian
coordinates but never in even the 95\% region in polar coordinates. This is a
consequence of the general \emph{concentration of measure}. Another way to look
at it is to transform the uniform prior density from cartesian to polar
coordinates. For the example of the single Wilson coefficient, say $\wilson{T}$,
the transformed density is proportional to the determinant of the Jacobian which
is $|\wilson{T}|$. In words, the uniform prior on $\mbox{Re}(\wilson{T})$ and
$\mbox{Im}(\wilson{T})$ favors larger values of $|\wilson{T}|$ even though we
consider it consensus in the community that smaller rather than larger values
are held reasonable because in the SM, $\wilson{T} = 0$. We suggest therefore
that the default prior be changed in the future.

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{Conclusions}

We have derived to date most stringent constraints on tensor and scalar
couplings that mediate $b\to s\bar\mu\mu$ utilising the latest measurements
of angular observables $F_H^\mu$ and the lepton forward-backward asymmetry
$A_{\rm FB}^\mu$ in $B^+\to K^+ \bar\mu\mu$ from LHCb \cite{Aaij:2014tfa},
supplemented by measurements of the branching ratios of $B_s\to \bar\mu\mu$ and
$B\to K^{(*)} \bar\mu\mu$. Both observables, $F_H^\mu$ and $A_{\rm FB}^\mu$,
belong to a class in which vector and dipole couplings that arise also in
the standard model (SM) are suppressed (mostly kinematically by $m_\ell /
\sqrt{q^2}$) w.r.t tensor and scalar couplings. We provide predictions for
analogous but not-yet-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$.

We find that the experimental measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
\item imposes by itself constraints on tensor couplings $|\wilson{T,\,T5}|
  < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter $|\wilson{T,\,T5}| < 0.33\,
  (0.43)$, even in the presence of nonstandard contributions in vector
  couplings.
\item allows for the first time to bound all four scalar couplings $\wilson{i}$
  with $i = S,\,S',\,P,\,P'$ due to it's complementarity to $\overline{\cal B}(B_s
  \to \bar\mu\mu)$. Even when taking into account destructive interference with
  vector couplings, $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and
  $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%)
  probability. Currently, the bounds from $F_H^\mu$ are not as strong as those
  from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a factor four. In the
  future, measurements at LHCb and Belle II will further tighten the bounds.

  Moreover, measurements of $F_H^e$ ($\ell = e$)
  will provide constraints on scalar couplings in the electron channel in
  the lack of measurements of the branching ratio of $B_s \to \bar{e}e$.
\end{enumerate}
Our updated bounds on complex-valued tensor and scalar couplings are summarised
in \reftab{tab:cTT5:1-dimCLs} and \reftab{tab:cSP:1-dimCLs}, accounting also for
interference effects with vector couplings. These bounds hold even in the most
general scenario of complex-valued tensor, scalar and vector couplings, showing
also that the data is able to bound the real and imaginary parts of all Wilson
coefficients simultaneously.

As a special case, we considered also the scenario arising from the SM augmented
by dimension 6 operators generalising existing studies to the case of complex-valued
couplings. In this scenario tensor couplings are absent and additional
relations between scalar couplings are enforced by the linear realisation of the
$SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.

Our study of yet-not-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ (see
\reftab{tab:postdictions}) shows that despite the current bounds on tensor couplings,
enhancements of two orders of magnitude over the SM predictions are allowed for
$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. On the other hand, current bounds
on scalar couplings from $B_s\to \bar\mu\mu$ and $F_H^\mu$ are already quite
restrictive allowing only for small deviations from SM predictions in
$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry
$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by nonvanishing width of the
$B_s$ meson can still take any value in the range $[-1,\, 1]$.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS}. Concerning form factor results from lattice, we thank Chris
  Bouchard and Matthew Wingate for communications on their results of $B\to K$
  \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form factors,
  respectively. We thank also David Straub for his support with LCSR results of
  $B\to K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
  DFG Cluster of Excellence "Origin and Structure of the Universe". The
  computations have been carried out on the computing facilities of the
  Computational Center for Particle and Astrophysics (C2PAP).
\end{acknowledgements}

>>>>

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling $\mbox{Re}(\wilson{T})$ of
    $F_H$ (first row) and ${\cal B}$ (second row) in $B^+ \to K^+ \bar\mu\mu$
    and ${\cal B}$ (third row), $J_{1c} + J_{2c}$ (fourth row), and $J_{1s}-3
    J_{2s}$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$ integrated over low- and
    high-$q^2$ bins. In the last two rows, the observables are rescaled by the
    lifetime of the $B$ meson for easier comparison with the branching
    ratios. The bands represent the theory uncertainties at 68\% and 95\%
    probability of the prior predictive distribution.  For comparison, two sets
    of bands are shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
    $\wilson[NP]{9} = -1.1$ (red), and an additional band of the latest 68\%
    confidence interval reported by LHCb (grey) if a measurement is
    available. \checked{} }
  \label{fig:FHvsCT}
\end{figure*}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  \checked{Fits and constraints}
  \label{sec:results}
}

@@

A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in cartesian
coordinates but never in even the 95\% region in polar coordinates\footnote{But
  the bin with lower edge $\wilson{T,T5} = 0$ is always in the 99\%
  region.}. This is a consequence of the general \emph{concentration of
  measure}. Another way to look at it is to transform the uniform prior density
from cartesian to polar coordinates. For the example of a single Wilson
coefficient, say $\wilson{T}$, the transformed density is proportional to the
determinant of the Jacobian which is $|\wilson{T}|$. Since the cartesian prior
boundaries are much larger than the regions of high likelihood, one could think
the value of the boundary is irrelevant but in fact it determines the peak of
the prior in polar coordinates. In other words, the uniform prior on
$\mbox{Re}(\wilson{T})$ and $\mbox{Im}(\wilson{T})$ favors larger values of
$|\wilson{T}|$ even though we consider it consensus in the community that
smaller rather than larger values are reasonable because $\wilson{T} = 0$ in the
SM. We suggest therefore that the default treatment be revised in the future to
include available prior knowledge.

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{\checked{Conclusions}}

We have derived the most stringent constraints to date on tensor and scalar
couplings that mediate $b\to s\bar\mu\mu$ transitions using the latest
measurements of angular observables $F_H^\mu$ and the lepton forward-backward
asymmetry $A_{\rm FB}^\mu$ in $B^+\to K^+ \bar\mu\mu$ from LHCb
\cite{Aaij:2014tfa}, supplemented by measurements of the branching ratios of
$B_s\to \bar\mu\mu$ and $B\to K^{(*)} \bar\mu\mu$. Both $F_H^\mu$ and $A_{\rm
  FB}^\mu$ belong to a class of observables in which vector and dipole
couplings---present in the standard model (SM)---are suppressed (mostly
kinematically by $m_\ell / \sqrt{q^2}$) with respect to tensor and scalar
couplings. We provide predictions for the equivalent but not-yet-measured
angular observables $J_{6c}$, $(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$ in
$B\to K^* (\to K\pi) \bar\mu\mu$.

In a Bayesian analysis of the complex-valued couplings of the effective theory,
we find that the measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
  \item imposes by itself bounds on tensor couplings $|\wilson{T,\,T5}|$ such
  that the upper bound of the smallest 68\% (95\%) credibility interval is
  $0.43\, (0.57)$, superseding previous bounds.  In combination with current
  data from $B\to K^* \bar\mu\mu$ and lattice $B\to K^*$ form factors, the
  bounds are lowered to 0.33 (0.43), even in the presence of nonstandard
  contributions in vector couplings.
  \item for the first time allows to bound all four scalar couplings
  $\wilson{i}$ with $i = S,\,S',\,P,\,P'$ due to it's complementarity to
  $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into account
  destructive interference with vector couplings, $|\wilson{i} + \wilson{i'}| <
  0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ with
  at least 68\% (95\%) probability. Currently, the bounds from $F_H^\mu$ are
  weaker than those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a
  factor of four. Future measurements of $F_H^\mu$ at LHCb and Belle II will
  further tighten the bounds.

  Moreover, measurements of $F_H^e$ ($\ell = e$) will provide constraints on
  scalar couplings in the electron channel in the absence of a direct
  determination of the branching ratio of $B_s \to \bar{e}e$.
\end{enumerate}
Our updated bounds on complex-valued tensor and scalar couplings are summarised
in \reftab{tab:cTT5:1-dimCLs} and \reftab{tab:cSP:1-dimCLs}, accounting also for
interference effects with vector couplings. These bounds hold even in the most
general scenario of complex-valued tensor, scalar, and vector couplings, showing
that the data are good enough to bound the real and imaginary parts of all
Wilson coefficients simultaneously.

As a special case, we considered the scenario arising from the SM augmented by
dimension-6 operators generalising existing studies to the case of
complex-valued couplings. In this scenario, tensor couplings are absent and
additional relations between scalar couplings are enforced by the linear
realisation of the $SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.

Our study of not-yet-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$,
and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ (see
\reftab{tab:postdictions}) shows that despite the current bounds on tensor
couplings, enhancements of up to two orders of magnitude over the SM predictions
are allowed for $(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in
reach of the LHCb analysis of the full phase I data set. Our bounds on scalar
couplings from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
restrictive permitting only small deviations from SM predictions in $(J_{1c} +
J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry
$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ is a sensitive probe to distinguish tensor
from scalar couplings; it can take on any value in the range $[-1,\, 1]$ for
nonzero scalar couplings but is fixed to one if the scalar couplings vanish.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS}. Concerning form factor results from lattice QCD, we thank
  Chris Bouchard and Matthew Wingate for communications on their results of
  $B\to K$ \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form
  factors. We thank also David Straub for his support with LCSR results of $B\to
  K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
  DFG Cluster of Excellence "Origin and Structure of the Universe". The
  computations have been carried out on the computing facilities of the
  Computational Center for Particle and Astrophysics (C2PAP).
\end{acknowledgements}
